Investigating Determinism of Gaming Engines for Autonomous Vehicle Verification

### 2019-12-19 paper/4_CaseStudy.tex
nothing much

Proceeding to step 2; there is about 20 different internal settings related to our context that can be tweaked in UE4; such as \textit{Enable Enhanced Determinsim}, \textit{PhysX Tree Rebuild}, \textit{Max Physics Delta Time} etc. By doing various inspections around them we did not notice much improvement or worsening in the simulation variance between test runs, therefore the internal settings option was disregarded.

@@

\subsection{Results And Discussion}\label{ResultsSection}
We start by analysing (step 5) the summary from all of the tests plotted in Figure~\ref{ExperimentsStressSummary}; where the x-axis represents the percentage of CPU + GPU utilisation and the y-axis shows the total mean devaition. 
This was calculated by averaging the variance between all of the different runs through out the simulation time for all of the agents, then taking the square root to obtain the total mean devaiton.
\begin{figure}[h]
    \centering
    \includegraphics[width=0.48\textwidth]{Other/Figures/ExperimentsStressSummary.pdf}
    \caption{Summary of total mean deviation for the different tests runs plotted against the different CPU + GPU stresses.}

@@

\begin{figure*}[h]
    \centering
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/CarsPeopleCollsionsCG25.pdf}
        \caption{}
        \label{CarsPeopleCollsionsCG25}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/CarsPeopleCollisionPrePost.pdf}
        \caption{}
        \label{CarsPeopleCollisionPrePost}
    \end{subfigure}
    \caption{Test ID 4 (a)Mean deviation over runs no. vs simulation time for 25\% stress. (b)Pre and post collision mean deviation over runs no. for different CPU + GPU stresses.}
\end{figure*}
Note the dotted red line in the plot shows the millimeter (mm) level. 
Below this level we assume that the level of simulation variance is very low for V\&V of CAV simulations purposes, that it is sufficient to assume the tests are deterministic and repeatable. 
This line can be moved up or down and it is entirely up to verification engineers where they want to define the level below which tests' variance is negligibale and it is suffcient to assume that tests are deterministic, but just for the sake of argument we chose it to be the millimeter level.

>>>>

Proceeding to step 2; there is about 20 different internal settings related to our context that can be tweaked in UE4; such as \textit{Enable Enhanced Determinsim}, \textit{PhysX Tree Rebuild}, \textit{Max Physics Delta Time} etc. By doing various inspections around them we did not notice much improvement or worsening in the simulation variance between test runs, therefore the internal settings option was disregarded. However, one of the options we used is synchronus mode with a fixed time step that is available in CARLA. This would make the simulator proceed to the next tick only when commanded to do so by our script, which makes runs' flow more consistently.

@@

\subsection{Results And Discussion}\label{ResultsSection}
We start by analysing (step 5) the summary from all of the tests plotted in Figure~\ref{ExperimentsStressSummary}; where the $x$-axis represents the percentage of CPU + GPU utilisation and the $y$-axis shows the total mean devaition. 
This was calculated by averaging the variance between all of the different runs through out the simulation time for all of the agents, then taking the square root to obtain the total mean devaiton.
\begin{figure}[h]
    \centering
    \includegraphics[width=0.48\textwidth]{Other/Figures/ExperimentsStressSummary.pdf}
    \caption{Summary of total mean deviation for the different tests runs plotted against the different CPU + GPU stresses.}

@@

\begin{figure*}[h]
    \centering
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/CarsPeopleCollsionsCG25.pdf}
        \caption{}
        \label{CarsPeopleCollsionsCG25}
    \end{subfigure}
    \begin{subfigure}{.49\textwidth}
        \includegraphics[width=1\textwidth]{Other/Figures/CarsPeopleCollisionPrePost.pdf}
        \caption{}
        \label{CarsPeopleCollisionPrePost}
    \end{subfigure}
    \caption{Test ID 4 (a)Mean deviation over runs no. vs simulation time for 25\% stress. (b)Pre and post collision mean deviation over runs no. for different CPU + GPU stresses.}
\end{figure*}
Note the dotted red line in the plot shows the millimeter (mm) level. 
Below this level we assume that the level of simulation variance is low enough that it would not affect our assertion checking for V\&V of CAV simulations purposes, that it is sufficient to assume the tests are deterministic and repeatable. 
This line can be moved up or down and it is entirely up to verification engineers where they want to define the level below which tests' variance is negligibale and it is suffcient to assume that tests are deterministic.
